exponential_BT

### 2025-04-03 inst/exponential_BT.Rmd
increase sample size

 print(system.time(parkrun01 <- single_like_fun(259, 177/259, N=1e3)))
 print(system.time(parkrun02 <- single_like_fun(305, 222/305, N=1e3)))
 print(system.time(parkrun03 <- single_like_fun(297, 206/297, N=1e3)))
#print(system.time(parkrun04 <- single_like_fun(241, 142/241, N=1e1)))
#print(system.time(parkrun05 <- single_like_fun(179, 118/179, N=1e1)))
#print(system.time(parkrun06 <- single_like_fun(338, 224/338, N=1e1)))
#print(system.time(parkrun07 <- single_like_fun(203, 128/203, N=1e1)))
```

```{r}
parkrun01
parkrun02
parkrun03
#parkrun04
#parkrun05
#parkrun06
#parkrun07
sum(parkrun01)
sum(parkrun02)
sum(parkrun03)
parkrun01 * parkrun02 *parkrun03
sum(parkrun01 * parkrun02 *parkrun03)
```

>>>>

 print(system.time(parkrun01 <- single_like_fun(259, 177/259, N=4e3)))
 print(system.time(parkrun02 <- single_like_fun(305, 222/305, N=4e3)))
 print(system.time(parkrun03 <- single_like_fun(297, 206/297, N=4e3)))
 print(system.time(parkrun04 <- single_like_fun(241, 142/241, N=4e3)))
 print(system.time(parkrun05 <- single_like_fun(179, 118/179, N=4e3)))
 print(system.time(parkrun06 <- single_like_fun(338, 224/338, N=4e3)))
 print(system.time(parkrun07 <- single_like_fun(203, 128/203, N=4e3)))
```

```{r}
parkrun01
parkrun02
parkrun03
parkrun04
parkrun05
parkrun06
parkrun07
sum(parkrun01)
sum(parkrun02)
sum(parkrun03)
parkrun01 * parkrun02 *parkrun03
sum(parkrun01 * parkrun02 *parkrun03)
```

1
